%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Stephen Zhaoming Su}{}

\position{BA, BCom, BSc(Hons)}
\address{Auckland, New Zealand}

\email{\href{mailto:szmsu2011@hotmail.co.nz}{\nolinkurl{szmsu2011@hotmail.co.nz}}}
\github{szmsu2011}
\linkedin{szmsu2011}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {June, 2023}
    {Stephen Zhaoming Su~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{employment}{%
\section{Employment}\label{employment}}

\begin{cventries}
    \cventry{Research Assistant Staff}{The University of Auckland}{Auckland, New Zealand}{Dec 2022 - Jun 2023}{\begin{cvitems}
\item Involved in developing a statistical programming package (iNZightVIT/iNZightTools) for data wrangling and manipulation
\item Completed the front-end and back-end implementation of functions in iNZightTS and iNZightTools on iNZight GUI
\item Supervisors: Prof Christopher J Wild, Dr Tom Elliott
\end{cvitems}}
    \cventry{Research Assistant Staff}{The University of Auckland}{Auckland, New Zealand}{Jan 2022 - Jun 2022}{\begin{cvitems}
\item Involved in developing a statistical programming package (iNZightVIT/iNZightTS) for visualising time series
\item Supervisors: Prof Christopher J Wild, Dr Tom Elliott
\end{cvitems}}
    \cventry{Teaching Assistant}{The University of Auckland}{Auckland, New Zealand}{Mar 2020 - Dec 2020}{\begin{cvitems}
\item Computer room tutor and marker of Statistical Computing (STATS 380) and Statistical Modelling (STATS 330).
\end{cvitems}}
    \cventry{Summer Research Scholar}{The University of Auckland}{Auckland, New Zealand}{Nov 2019 - Apr 2020}{\begin{cvitems}
\item Involved in a research project in developing statistical computing tools for Visualising Multivariate Data (SCI078).
\item Supervisor: Prof Christopher J Wild
\end{cvitems}}
    \cventry{Index and Quantitative Investment Analyst Intern}{GF Fund Management Co., Ltd.}{Guangzhou, China}{Dec 2018}{\begin{cvitems}
\item Assisted in data analytics workflow and preparation works.
\end{cvitems}}
\end{cventries}

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{BSc(Hons) in Statistics with First Class Honours}{The University of Auckland}{Auckland, New Zealand}{Mar 2021 - Feb 2022}{\begin{cvitems}
\item Recipient of the University of Auckland Postgraduate Honours Scholarship.
\item Studied data visualisation, frequentist and Bayesian inferences, multivariate analysis, stochastic processes and statistical computing with R.
\item Honours research project was to develop a data storytelling dashboard for exploring Auckland air quality using R.
\end{cvitems}}
    \cventry{BA in Statistics, BCom in Finance and Information Systems}{The University of Auckland}{Auckland, New Zealand}{Jul 2017 - Dec 2020}{\begin{cvitems}
\item Recipient of the University of Auckland Academic Potential Scholarship.
\item Recipient of the University of Auckland Summer Research Scholarship.
\item Recipient of the Senior Scholar Award in the Faculty of Arts.
\item Studied stochastic modelling, time series analysis, statistical modelling and statistical computing using R and SAS, in Statistics.
\item Studied advanced financial management, modern investment theory and risk management, in Finance.
\item Studied information security, data visualisation using Tableau and enterprise systems with SAP ERP, in Information Systems.
\item Obtained first in class in 5 courses.
\end{cvitems}}
\end{cventries}

\hypertarget{software-development}{%
\section{Software development}\label{software-development}}

\begin{cvhonors}
    \cvhonor{}{\textbf{iNZightTS}: Author \newline Provides analysis and data visualisation tools for exploring time series data used by iNZightVIT/iNZight.}{}{2022\newline}
    \cvhonor{}{\textbf{iNZightTools}: Author \newline Provides data wrangling and manipulation helper functions for data science practices in iNZightVIT/iNZight.}{}{2023\newline}
    \cvhonor{}{\textbf{iNZight}: Contributor \newline Graphical user interface of the iNZight application, which provides tools for data manipulation, exploratory data analysis, multi-variable graphics, time series analysis and linear models.}{}{2023\newline}
\end{cvhonors}



\end{document}
